\addcontentsline{toc}{chapter}{\bibname}	% Добавляем список сей в оглавление

\begin{thebibliography}{20} % максимальное число указывается книг здесь (20)
	% -------------------------------------------------------------------------------------------------------------------- %

	\bibitem{bib1} 
	Storn R, Price K (1995) 
	Differential evolution a simple and efficient heuristic for global optimization over continuous spaces. Technical Report TR-95-012, ICSI
	
	\bibitem{bib2} 
	Konstantin Kozlov and Samsonov, A. (2011). 
	DEEP – Differential Evolution Entirely Parallel Method for Gene Regulatory Networks. Journal of Supercomputing, 57:172–178
	
	\bibitem{bib3}
	Н.В. Иваниcенко, Е.Л. Мищенко, И.P. Акбеpдин, П.C. Деменков, В.А. Лиxошвай, К.Н. Козлов, Д.И. Тодоpов, М.Г. Cамcонова, А.М. Cамcонов, Н.А. Колчанов, В.А. Иваниcенко (2013) 
	Репликация cубгеномного pепликона виpуcа гепатита C в пpиcутcтвии ингибитоpов NS3-пpотеазы: cтоxаcтичеcкая модель, биофизика, том 58, вып. 5, c. 758-774

	\bibitem{bib4}
	Konstantin Kozlov, Surkova, S., Myasnikova, E., Reinitz, J., and Samsonova, M. (2012). 
	Modeling of gap gene expression in drosophila Kruppel mutants. PLoS Computational Biology. doi:10.1371/journal.pcbi.1002635

	\bibitem{bib5}
	Konstantin Kozlov, Nikita Ivanisenko, Vladimir Ivanisenko, Nikolay Kolchanov, Maria Samsonova, and Alexander M.Samsonov (2013), 
	«Enhanced Differential Evolution Entirely Parallel Method for Biomedical Applications», LNCS 7979, Parallel Computing Technologies, Victor Malyshkin (Ed.), 
	Springer 2013, ISSN 0302-9743, Proceedings of the 12th International Conference, PaCT 2013, St.Petersburg, Russia, September/October 2013, pp. 409-416.

	\bibitem{bib6}
	Steiert B, Raue A, Timmer J, Kreutz C (2012) 
	Experimental Design for Parameter Estimation of Gene Regulatory Networks. PLoS ONE 7(7): e40052. doi:10.1371/journal.pone.0040052
	
	\bibitem{bibZaharie}
	D. Zaharie
	Control of Population Diversity and Adaptation in Differential Evolution Algorithms, 
	in R. Matousek, P. Osmera (eds.), Proc. of Mendel 2003, 9th International Conference on Soft Computing, Brno, pp. 41-46, 2003.
	
	\bibitem{bibTM}
	Fan H-Y, Lampinen J (2003) 
	A trigonometric mutation operation to differential evolution. J Glob Optim 27:105–129
	
	\bibitem{bibDREAM}
	Описание DREAM6 \href{http://www.the-dream-project.org/challenges/dream6-estimation-model-parameters-challenge}{the-dream-project.org}

	\bibitem{bibGit}
	Модели генных сетей (язык R) \href{https://github.com/latur/DREAM6}{github.com/latur/DREAM6}

	% -------------------------------------------------------------------------------------------------------------------- %
\end{thebibliography}
